\vspace{1.0cm} \LARGE \bf Structured population models demystify MERS-CoV epidemiology

### 2017-07-08 mers-structure.tex
forgot an important scolding

\subsection*{Sequence data as a universal epidemiology tool}
As the field of epidemiology enters the age of genomics sequence data are likely to be brought to the forefront of epidemiological investigations.
At a relatively low price, sequence data offer the combined benefits of diagnostics and typing, whilst also offering insight into a pathogen's evolutionary history.
With a small amount of metadata, primarily collection dates and features of interest, such as location or host, much can be revealed through phylogenetic clustering of sequences, or absence thereof.
This was used to great effect towards the end of the Ebola virus epidemic in West Africa, where the final transmission chains were tracked and confirmed as such with sequence data \citep{arias_rapid_2016}.
Although sequence data can be collected for multiple reasons and used to address different questions, sequence data are a fundamental unit of ground truth, which allows data from wildly different studies to be combined trivially.
In fact it has often been the combination of data from distinct populations and different time periods that yielded most insight in the past \citep{dudas_virus_2017}.

>>>>

\subsection*{Sequence data as a universal epidemiology tool}
As the field of epidemiology enters the age of genomics sequence data are likely to be brought to the forefront of epidemiological investigations.
At a relatively low price, sequence data offer the combined benefits of diagnostics and typing, whilst also offering insight into a pathogen's evolutionary history.
With a small amount of metadata, primarily collection dates and features of interest, such as location or host, much can be revealed through phylogenetic clustering of sequences, or absence thereof.
This was used to great effect towards the end of the Ebola virus epidemic in West Africa, where the final transmission chains were tracked and confirmed as such with sequence data \citep{arias_rapid_2016}.
Although sequence data can be collected for multiple reasons and used to address different questions, sequence data are a fundamental unit of ground truth, which allows data from wildly different studies to be combined trivially\lmc{TRIVIALLY???}.
In fact it has often been the combination of data from distinct populations and different time periods that yielded most insight in the past \citep{dudas_virus_2017}.
